Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-08-31 reanalysis-4-propensity_scores.qmd
deps

    # Ensure lapse is properly formatted as numeric 0/1
    if ("lapse" %in% names(imp_data)) {
      if (is.factor(imp_data$lapse)) {
        # Convert factor to numeric via character to avoid level issues
        imp_data$lapse <- as.numeric(as.character(imp_data$lapse))
      } else if (is.character(imp_data$lapse)) {
        imp_data$lapse <- as.numeric(imp_data$lapse)
      } else if (is.logical(imp_data$lapse)) {
        imp_data$lapse <- as.numeric(imp_data$lapse)
      }

      # Ensure values are 0 or 1
      if (any(!imp_data$lapse %in% c(0, 1, NA))) {
        stop(paste("Lapse variable contains values other than 0, 1, or NA in imputation", i))
      }
    } else {
      stop(paste("Lapse variable not found in imputation", i))
    }

>>>>

    # Ensure ever_lapse_binary is properly formatted as numeric 0/1
    if ("ever_lapse_binary" %in% names(imp_data)) {
      if (is.factor(imp_data$ever_lapse_binary)) {
        # Convert factor to numeric via character to avoid level issues
        imp_data$ever_lapse_binary <- as.numeric(as.character(imp_data$ever_lapse_binary))
      } else if (is.character(imp_data$ever_lapse_binary)) {
        imp_data$ever_lapse_binary <- as.numeric(imp_data$ever_lapse_binary)
      } else if (is.logical(imp_data$ever_lapse_binary)) {
        imp_data$ever_lapse_binary <- as.numeric(imp_data$ever_lapse_binary)
      }

      # Ensure values are 0 or 1
      if (any(!imp_data$ever_lapse_binary %in% c(0, 1, NA))) {
        stop(paste("ever_lapse_binary variable contains values other than 0, 1, or NA in imputation", i))
      }
    } else {
      stop(paste("ever_lapse_binary variable not found in imputation", i))
    }
